Untitled

### 2023-10-16 code/analysis_Redo.Rmd
Making nicer figures

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
library(tigris)
```

@@

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") , 
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience"), common.legend = TRUE, nrow = 1 ) 
p0

@@

p <- df.z.dist.plot %>% 
  filter(DistToClosestSite < 200) %>% 
  ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
  geom_point(aes(size = DistToClosestSite, colour = DistToClosestSite)) + 
  scale_colour_gradientn(colours = c("green","lightblue","purple"),
                         values = c(1.0,0.7,0.1,0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
  theme_minimal() + ylab("Log Population Density of New Zip Code") + 
  xlab("Log Population Density of Nearest Service Area Zip Code") + 
  labs(color = "Distance Travelled to\nOpenNew Site (km)") + 
  guides(size = FALSE) + xlim(0.5, 11.5) + ylim(0.5, 11.5)
p

@@

## Primary effects by distance rival travelled
```{r}
set.seed(123)
df.dist <- df.core2 %>% 
  left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite, Density.NewZip), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Dist.random = sample(size = 1, unique(df.z.dist.plot$DistToClosestSite / df.z.dist.plot$Density.NewZip), replace = TRUE), 
         Dist.random = ifelse(Att > 0, DistToClosestSite / Density.NewZip, Dist.random))

#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.5), na.rm = TRUE)

splits1 <- c(min(df.dist$Dist.random, na.rm = TRUE)-1, splits)
splits2 <- c(splits, max(df.dist$Dist.random, na.rm = TRUE))

did.dist <- c(0, 0, 0, 0)
for (g in 1:(length(splits) + 1)){
  for (j in 10:12){

  df.temp <- df.dist[,c(1:9, j, 13:ncol(df.dist))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(Dist.random > splits1[g] & Dist.random <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )

  did.dist <- rbind(did.dist, outcomes$coeftable)

did.dist <- did.dist[-1,]
rownames(did.dist) <- NULL

data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.dist[,1]), 
      SD = as.numeric(did.dist[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by Distance Traveled")
```

@@

  left_join(census %>% 
              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
  #mutate(Sites = log(Sites + 1)) %>% 
  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(NumberofPatients > 100 | NumberofPatients / TotalPop > 0.01)

@@

zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
zp

@@

@@

@@

df.p %>% 
  filter(Year.y == Att.z) %>% 
  mutate(xcoor = xcoor / Radius, 
         ycoor = ycoor / Radius, 
         popcenter.x = popcenter.x / Radius, 
         popcenter.y = popcenter.y / Radius) %>% 
 #filter(Zip == "43604") %>%  #43604
  ggplot(aes(x = xcoor, y = ycoor, color = ClinicType)) + 
  #geom_rect(aes(xmin = -SquareSide / 2, xmax = SquareSide / 2, ymin = -SquareSide / 2, ymax = SquareSide / 2), fill = "blue", alpha = 0.2, color = NA) + 
  geom_rect(aes(xmin = -1, xmax = 1, ymin = -1, ymax = 1), fill = "lightgrey", alpha = 0.2, color = NA) + 
  geom_point(position=position_jitter(width=0.05, height=0.05)) + xlim(-2, 2) + ylim(-2, 2) + 
  geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") + facet_wrap(~Zip)

@@

    df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
      mutate(Type = "Incumbent") %>% 
      rbind(df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.x" = "BHCMISID", "Year")) %>% mutate(Type = "Rival")) %>% 
        mutate(Quality = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100) %>% 
      mutate(quick_ratio = as.numeric(quick_ratio),
             Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities) %>% 
      mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
      select(Type, Quality, Total, Altman) %>% 
          tbl_summary(by = Type, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
  add_p()

>>>>

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
library(tigris)
library(usmap)
```

@@

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  #filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  #filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  #filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, nrow = 1 ) 
p0

@@

p <- df.z.dist.plot %>% 
  filter(DistToClosestSite > 25) %>% 
  ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
  geom_point(aes(size = DistToClosestSite, colour = DistToClosestSite)) + 
  scale_colour_gradientn(colours = c("green","lightblue","purple"),
                         values = c(1.0,0.7,0.1,0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
  theme_minimal() + ylab("Log Population Density of New Zip Code") + 
  xlab("Log Population Density of Nearest Service Area Zip Code") + 
  labs(color = "Distance Travelled to\nOpenNew Site (km)") + 
  guides(size = FALSE) + xlim(0.5, 11.5) + ylim(0.5, 11.5)
p

@@

@@

  left_join(census %>% 
              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
  #mutate(Sites = log(Sites + 1)) %>% 
  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) %>% 
  mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites))#%>% filter(NumberofPatients > 100 | NumberofPatients / TotalPop > 0.01)

@@

zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
zp <- ggarrange(zp3, zp4, common.legend = TRUE)
zp

@@

p.rival.dist <- df.z.dist %>% 
  arrange(DistToClosestSite) %>% 
    ggplot(aes(x=DistToClosestSite)) + geom_histogram(binwidth = 1, fill="lightgrey", color="white") + xlim(0,150) + 
  #ylim(0, 25) + 
   #scale_x_log10(name = 'Number of planned tours', breaks=c(1,5,10,50,100,200))+
   stat_bin(aes(y=cumsum(..count..)/10), binwidth = 1, geom="line",color="blue") + 
   scale_y_continuous(name = 'Number of Rivals', sec.axis = sec_axis(~./81*1000, name = "Cummulative percentage (%)")) + 
  theme_tufte_revised() + ggtitle("FQHC Rivals by Distance from Service Area to New Competitive Zip") + xlab("Distance Travelled (km)")

p.rival.dist

@@

## Map of where competitive zip codes are

#eq_transformed <- usmap_transform(earthquakes)

eq_transformed <- usmap_transform(df.z.dist %>% 
  left_join(zip.centroids %>% rename(lon = X, lat = Y) , by = c("Zip" = "ZipCode"))) %>% 
  mutate(`Distance Travelled` = ifelse(DistToClosestSite > 25, ">25km", "<25km"))

plot_usmap() +
  geom_point(data = eq_transformed, aes(x = x, y = y, color = `Distance Travelled`)) +
  labs(title = "Competitive Zip Codes",
       subtitle = "By Distance Traveled by Rival") +
  theme(legend.position = "right")
```

@@

df.p %>% 
  filter(Year.y == Att.z) %>% 
  mutate(xcoor = xcoor / Radius, 
         ycoor = ycoor / Radius, 
         popcenter.x = popcenter.x / Radius, 
         popcenter.y = popcenter.y / Radius) %>% 
 #filter(Zip == "43604") %>%  #43604
  ggplot(aes(x = xcoor, y = ycoor, color = ClinicType)) + 
  #geom_rect(aes(xmin = -SquareSide / 2, xmax = SquareSide / 2, ymin = -SquareSide / 2, ymax = SquareSide / 2), fill = "blue", alpha = 0.2, color = NA) + 
  geom_rect(aes(xmin = -1, xmax = 1, ymin = -1, ymax = 1), fill = "lightgrey", alpha = 0.2, color = NA) + 
  geom_point(position=position_jitter(width=0.05, height=0.05)) + xlim(-2, 2) + ylim(-2, 2) #+ 
  #geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") #+ facet_wrap(~Zip)

@@

    df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
      mutate(Type = "Incumbent") %>% 
      rbind(df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.x" = "BHCMISID", "Year")) %>% mutate(Type = "Rival")) %>% 
        mutate(Quality = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100) %>% 
      mutate(quick_ratio = as.numeric(quick_ratio),
             Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities) %>% 
      mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
      select(Type, Quality, Total, Altman, Pct.NHA:Pct.COM) %>% 
          tbl_summary(by = Type, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
  add_p()
